Advances in Artificial Intelligence for Data Visualization: Automated Reading of Residual Plots with Computer Vision

### 2023-04-17 Milestone_presentation_2/Milestone_presentation_2/Untitled.Rmd
find the residual plot and provide a lineup

.center[
.caption[
Fig. 1: _One classically good looking residual plot but rejected by the RESET test with $p\text{-value} = `r format(round(this_p_value$p_value, digits = 3), nsmall = 3)`$._
]
]

@@

While such rejections may be **statistically correct**, their sensitivity may render the results **impractical**.

@@

# Reading residual plot vs. conventional statistical testing

(Use non-linearity as the example)

How people read residual plot?
How statistical testing detect residual departures?

>>>>

.center[
.caption[
Fig. 2: _One classically good looking residual plot but rejected by the RESET test with $p\text{-value} = `r format(round(this_p_value$p_value, digits = 3), nsmall = 3)`$._
]
]

@@

While such rejections may be **statistically correct**, their **sensitivity** may render the results **impractical**.

@@

.center[
# 💔False visual discoveries💔
]

```{r}
set.seed(10131)
mod <- heter_model(b = 0, x = rand_lognormal())
ori_dat <- mod$gen(300)

ori_dat %>%
  VI_MODEL$plot(theme = theme_light(base_size = 12)) +
  xlab("Fitted values") +
  ylab("Residuals")
```

.center[
.caption[
Fig. 3: _Residual plot of a simple linear regression._
]
]

Can you find the evidence on heteroskedasticity?

- Vertical spread of the points varies with the fitted values.

However, the residuals are actually obtained from a **correctly specified classical normal linear model**!

**Unsecured** and **unconfirmed** visual discoveries will lead to **over or under-interpretations of the data**.

```{r}
set.seed(10131)
mod$gen_lineup(300, k = 20, pos = 8) %>%
  filter(null != FALSE) %>%
  bind_rows(ori_dat %>% mutate(k = 8, null = FALSE)) %>%
  VI_MODEL$plot_lineup(theme = theme_light(base_size = 12),
                       remove_grid_line = TRUE,
                       remove_axis = TRUE)
```
.center[
.caption[
Fig. 4: _Lineup of residual plots._
]
]
